How to Write Theses\\ With Two Line Titles

### 2019-08-07 chapters/litReview/synthesisMatrix.tex
new

  Semi-Proving: An Integrated Method for Program Proving, Testing, and Debugging             &
  “Siemens suite of programs” specifically “replace program”: performs regular expression matching and substitutions.                                                                           &
  Given the text 'ab', replacing 'a' with 'x' is equivalent to replacing non-'b' with 'x'. \par\medskip
  'char' and '[char]' are equivalent with the exception of a few wildcards. \par\medskip
  Regular expressions that involve square brackets are equivalent. \par\medskip
  Use '?*' to match the entire input string.                                                             &
  Proof of concept. \par\medskip
  Supports automatic debugging through the identification of constraints for failure-causing inputs.
  \\

@@

  Metamorphic Testing and Beyond             &
  A laplace equation with Dirichlet boundary Conditions: “alternating direction implicit” method                                        &
  Beyond identity relations: Convergence                                          &
  Selecting useful MRs. \par\medskip
  Stronger may not necessarily be better than weaker ones. \par\medskip
  Provides guidelines.  \\

>>>>

  Semi-Proving: An Integrated Method for Program Proving, Testing, and Debugging             &
  "Siemens suite of programs" specifically "replace program": performs regular expression matching and substitutions.                                                                           &
  Given the text 'ab', replacing 'a' with 'x' is equivalent to replacing non-'b' with 'x'. \par\medskip
  'char' and '[char]' are equivalent with the exception of a few wildcards. \par\medskip
  Regular expressions that involve square brackets are equivalent. \par\medskip
  Use '?*' to match the entire input string.                                                             &
  Proof of concept. \par\medskip
  Supports automatic debugging through the identification of constraints for failure-causing inputs.
  \\

@@

  Metamorphic Testing and Beyond             &
  A laplace equation with Dirichlet boundary Conditions: "alternating direction implicit" method                                        &
  Beyond identity relations: Convergence                                          &
  Selecting useful MRs. \par\medskip
  Stronger may not necessarily be better than weaker ones. \par\medskip
  Provides guidelines.  \\
